### 2017-09-28 TF-vldb2018/sec-intro.tex

 Graph simulation \cite{infsimu95} and its extensions have been introduced for graph pattern matching~\cite{FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}, in which {\em strong simulation} introduces duality and locality into simulation~\cite{MaCFHW14}, and shows a good balance between its computational complexity and its ability to preserve graph topology. Furthermore, \cite{FanCount16} already adopts capacity bounds on the edges of pattern graphs via subgraph isomorphism, and \cite{FanWWXin13} uses graph pattern matching to find single experts, instead of a team of experts. In this study, team simulation is proposed for team formation as an extension of graph simulation and strong simulation on undirected graphs with capacity constraints on pattern graphs.

>>>>

 Graph simulation \cite{infsimu95} and its extensions have been introduced for graph pattern matching~\cite{FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}, in which {\em strong simulation} introduces duality and locality into simulation~\cite{MaCFHW14}, and shows a good balance between its computational complexity and its ability to preserve graph topology. Furthermore, \cite{FanCount16} already adopts capacity bounds on the edges of pattern graphs via subgraph isomorphism, and \cite{FanWWXin13} uses graph pattern matching to find single experts, instead of a team of experts. In this study, team simulation is proposed for team formation as an extension of graph simulation and strong simulation on undirected graphs with capacity constraints on the nodes of pattern graphs.
